### 2017-03-28 thesis/results/results.tex
tmp commit

\begin{figure}[tb!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/creighton_mg_heatmap1}
	\caption[Obesity metagene from \citet{Creighton2012} study and sample gene expression in CR data] {Heatmap showing the obesity metagene from the \citet{Creighton2012} study with the sample gene expressions of the obesity associated genes in the CR data.
	Level of expression is represented in the top right histogram, where low and high gene expression are colour-coded with blue and red, respectively.
	Each row of the heatmap represents a gene from the obesity associated genetic signature, and each column of the heatmap represents a sample from the CR data.
	The obesity associated metagene scores of the samples are shown as a separate row at top of the heatmap, and the tree diagram of the hierarchical clustering of the genes is shown on the left of the heatmap.
	For clarity, the sign of the metagene scores were reversed in order to match the results from the \citet{Creighton2012} study.}
	\label{fig:crmetaheat}
\end{figure}

>>>>

\begin{figure}[tb!]
	\centering
	\includegraphics[page=3,width=0.8\linewidth]{results1/creighton_mg_heatmap1}
	\caption[Obesity metagene from the \citet{Creighton2012} study and sample gene expression in CR data] {Heatmap showing the obesity metagene from the \citet{Creighton2012} study with the sample gene expressions of the obesity associated genes in the CR data.
	Level of expression is represented in the top right histogram, where low and high gene expression are colour-coded with blue and red, respectively.
	Each row of the heatmap represents a gene from the obesity associated genetic signature, and each column of the heatmap represents a sample from the CR data.
	The obesity associated metagene scores of the samples are shown as a separate row at top of the heatmap, and the tree diagram of the hierarchical clustering of the genes is shown on the left of the heatmap.
	For clarity, the sign of the metagene scores were reversed in order to match the results from the \citet{Creighton2012} study.}
	\label{fig:crmetaheat}
\end{figure}

### 2017-03-28 thesis/results/results2.tex
tmp commit

\begin{figure}[htpb]
	\centering
	\includegraphics[page=76,width=0.45\linewidth]{results2/allmeta_rma_vs_mas}
	\includegraphics[page=100,width=0.45\linewidth]{results2/allmeta_rma_vs_mas}
	\caption[Comparison of the pathway metagenes generated in the \acrshort{mas} normalised GT data set from the application of the transformation matrices derived from either the \acrshort{rma} or \acrshort{mas} normalised GT data]{Comparison of the pathway metagenes generated in the \acrshort{mas} normalised GT data set from the application of the transformation matrices derived from either the \acrshort{rma} or \acrshort{mas} normalised GT data.
	Only the \gls{pr} (left) and the \gls{tgfb}  (right) pathway metagenes are shown.
	The scatter plots for the other pathway metagenes are shown in \cref{sec:normalisation_method_for_pathway_associated_genetic_signature_transformation_matrices}.
	}
	\label{fig:gt_rma_vs_mas}
\end{figure}

@@

\begin{table}[htpb]
	\centering
	\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the Cr obesity, using only the patient \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the Cr obesity, using only the patient \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
	\label{tab:lm_pr_only}
	\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
				\hline
				\hline
				\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.477  & {\bfseries \num{6.06d-7}}\tnote{1}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002 & 0.586\\
                                                                           & \gls{pr}   & 0.478  & {\bfseries \num{6.35d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.085 & 0.176\\
                                                                           & Overweight & -0.011 & 0.875\\
                                                                           & \gls{pr}   & 0.471  & {\bfseries \num{8.25d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007  & 0.237\\
                                                                           & Obese      & -0.188 & 0.081\\
                                                                           & Overweight & -0.049 & 0.516\\
                                                                           & \gls{pr}   & 0.459  & {\bfseries \num{1.54d-6}}\\
				\hline
				\hline
			\end{tabular}
			\begin{tablenotes}
				\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
				\end{footnotesize}
			\end{tablenotes}
	\end{threeparttable}
\end{table}

>>>>

\begin{figure}[htpb]
	\centering
	\includegraphics[page=76,width=0.45\linewidth]{results2/allmeta_rma_vs_mas}
	\includegraphics[page=100,width=0.45\linewidth]{results2/allmeta_rma_vs_mas}
	\caption[Comparison of the pathway metagenes generated in the \acrshort{mas} normalised GT data set from the application of TMs, derived from either the \acrshort{rma} or \acrshort{mas} normalised GT data]{Comparison of the pathway metagenes generated in the \acrshort{mas} normalised GT data set from the application of the transformation matrices derived from either the \acrshort{rma} or \acrshort{mas} normalised GT data.
	Only the \gls{pr} (left) and the \gls{tgfb}  (right) pathway metagenes are shown.
	The scatter plots for the other pathway metagenes are shown in \cref{sec:normalisation_method_for_pathway_associated_genetic_signature_transformation_matrices}.
	}
	\label{fig:gt_rma_vs_mas}
\end{figure}

@@

\begin{table}[htpb]
	\centering
	\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the Cr obesity, using only the patient \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the Cr obesity, using only the patient \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
	\label{tab:lm_pr_only}
	\begin{threeparttable}
			\begin{tabular}{llrS}
				Linear Model & Variables & Estimate & {P-value}\\
				\hline
				\hline
				\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.477  & {\bfseries \num{6.06d-7}}\tnote{1}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002 & 0.586\\
                                                                           & \gls{pr}   & 0.478  & {\bfseries \num{6.35d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.085 & 0.176\\
                                                                           & Overweight & -0.011 & 0.875\\
                                                                           & \gls{pr}   & 0.471  & {\bfseries \num{8.25d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007  & 0.237\\
                                                                           & Obese      & -0.188 & 0.081\\
                                                                           & Overweight & -0.049 & 0.516\\
                                                                           & \gls{pr}   & 0.459  & {\bfseries \num{1.54d-6}}\\
				\hline
				\hline
			\end{tabular}
			\begin{tablenotes}
				\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
				\end{footnotesize}
			\end{tablenotes}
	\end{threeparttable}
\end{table}
